---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


##Load our libraries

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
```

## Loading and preprocessing the data

```{r}
df<-read.csv("activity.csv", stringsAsFactors = FALSE,colClasses = c("numeric","Date","integer"), na.strings = "NA")
df<-df %>% filter(!is.na(steps)) 
```


## What is mean total number of steps taken per day?
Note: For this part of the assignment, you can ignore the missing values in the dataset.

1. Calculate the total number of steps taken per day
```{r, warning=FALSE}
steps_daily<-df %>% group_by(date) %>% summarise(TotalSteps = sum(steps)) %>% ungroup()
head(steps_daily)
```

2. If you do not understand the difference between a histogram and a barplot, research the difference between them. Make a histogram of the total number of steps taken each day

```{r}
ggplot(steps_daily,aes(x=TotalSteps)) + geom_histogram(bins = 5) + 
  labs(title ="Histogram of total number of steps per day") + xlab("Total number of steps in a day")
```


3. Calculate and report the mean and median of the total number of steps taken per day

```{r echo=TRUE}
mean(steps_daily$TotalSteps)
median(steps_daily$TotalSteps)
```


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
