---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


##Load our libraries

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
```
## Loading and preprocessing the data

```{r}
df_all<-read.csv("activity.csv", stringsAsFactors = FALSE,colClasses = c("numeric","Date","integer"), na.strings = "NA")
df<-df_all %>% filter(!is.na(steps)) 
```

## What is mean total number of steps taken per day?
Note: For this part of the assignment, you can ignore the missing values in the dataset.

1. Calculate the total number of steps taken per day
```{r, warning=FALSE}
steps_daily<-df %>% group_by(date) %>% summarise(TotalSteps = sum(steps)) %>% ungroup()
head(steps_daily)
```

2. Make a histogram of the total number of steps taken each day
```{r}
ggplot(steps_daily,aes(x=TotalSteps)) + geom_histogram(bins = 5) + 
  labs(title ="Histogram of total number of steps per day") + xlab("Total number of steps in a day")
```

3. Calculate and report the mean and median of the total number of steps taken per day

```{r}
mean(steps_daily$TotalSteps)
median(steps_daily$TotalSteps)
```


## What is the average daily activity pattern?

1. Make a time series plot (i.e.type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}
avg_daily<- df %>% group_by(interval) %>% summarise(avg_steps = mean(steps)) %>% ungroup()
plot(x = avg_daily$interval, y = avg_daily$avg_steps, type="l",
     main="Average number of steps over all days", xlab="Interval", 
     ylab="Average number of steps")
```

2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r warning=FALSE}
avg_daily[which.max(avg_daily$avg_steps),] 
```



## Imputing missing values

1. Calculate and report the total number of missing values in the dataset 
```{r warning=FALSE}
sum(is.na(df_all$steps))
```

2. Devise a strategy for filling in all of the missing values in the dataset, in our case we will use the mean of steps without `NA` values.
```{r warning=FALSE}
mean_steps<-mean(df$steps)
```


3. Create a new dataset that is equal to the original dataset but with the missing data filled in.
```{r warning=FALSE}
df_fill<- df_all %>% mutate(steps = if_else(is.na(df_all$steps),mean_steps,steps))
```

4.Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day. 
```{r warning=FALSE}
steps_daily_fill<-df_fill %>% group_by(date) %>% summarise(TotalSteps = sum(steps)) %>% ungroup()

ggplot(steps_daily_fill,aes(x=TotalSteps)) + geom_histogram(bins = 5) + 
  labs(title ="Histogram of total number of steps per day") + xlab("Total number of steps in a day")

mean(steps_daily_fill$TotalSteps)  
median(steps_daily_fill$TotalSteps)  

```
if we take these two values and compare with previous values, we can see a small difference in the median, because it change from `10,765` to `10,766.19` and of course this is due to the estimation of the missing values.


## Are there differences in activity patterns between weekdays and weekends?
